%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                                 %
%         MODELO DE TESE/DISSERTAÇÃO - INSTITUTO DE FÍSICA - UNIVERSIDADE FEDERAL DE GOIÁS        %
%                                by carriunix (stardate 1601.01)                                  %
%                                 marcuscarriao at gmail dot com                                  %
%                                                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                                 %
%                                      AVISOS (Leia com atenção)                                  %
%                                                                                                 %
% Este é um modelo NÃO OFICIAL para Teses e Dissertações para alunos do IF-UFG. A intenção deste  %
% material é simplificar, padronizar e personalizar esses trabalhos científicos no âmbito da re-  %
% ferida instituição. Antes de começar a usar este modelo tenha em mente:                         %
%     (i) Ele não segue todas as normas da ABNT (apenas as esteticamente aceitáveis).             %
%    (ii) O modelo é composto por 4 arquivos: UFGmodelo.tex, UFGpreambulo.tex, UFGlogo.png e      %
% IFlogo.png (se você não tem algum desses, provavelmente vai ter problemas)                      %
%   (iii) Este modelo não constitui uma "classe", ele usa um arquivo de definições para ser       %
% usado "sobre" a classe "report" (nativo).                                                       %
%    (iv) Uma série de pacotes serão necessários (todos parte do TeXlive), consulte as primei-    %
% ras linhas do arquivo UFGpreambulo.tex para conhecê-los pessoalmente.                           %
%     (v) Este não é um modelo "for dummies": se você fizer coisa errada... vai dar errado!       %
%    (vi) Siga as instruções abaixo usando como referências as linhas do arquivo não modificado.  %
%                                                                                                 %
%                              INSTRUÇÕES (Leia com mais atenção ainda)                           %
%                                                                                                 %
%   l(76): Escolha as opções que achar conveniente ("oneside" e "twoside" estão disponíveis, mas  %
% os elementos do PRÓLOGO serão sempre "oneside"), mas não altere a classe. Sugiro que você con-  %
% tinue usando o tamanho 12pt (ABNT).                                                             %
%   l(77): Verifique a codificação que você está utilizando.                                      %
%   l(78): Seleção da fonte Times, sugerida por ser estéticamente mais agradável. Se você prefe-  %
% rir usar a Arial (ABNT), comente essa linha e descomente a l(79).                               %
%   l(81): Carregamento do preâmbulo. Verifique opções no próprio arquivo.                        %
%   l(83): Por default, esse é um modelo para doutorandos, se você é um mestrando, comente essa   %
% linha e descomente a seguinte l(84).                                                            %
%   l(85): Entre com o título da sua Tese/Dissertação.                                            %
%   l(86): Caso exista um subtítulo, descomente e preencha esta linha.                            %
%   l(87): Seu nome.                                                                              %
%   l(88): Nome do orientador já com a titulação.                                                 %
%   l(89): Cidade.                                                                                %
%   l(90): Ano com quatro dígitos.                                                                %
%   l(91): Data da defesa no formato "01 de janeiro de 0001"                                      %
%   l(92): Escreva a dedicatória (usando "\\" para saltar linha intencionalmente) ou use o coman- %
% do "\input{file}".                                                                              %
%   l(93): Escreva o texto de uma citação, que aparecerá em itálico e entre aspas.                %
%   l(94): Nome do autor da citação, que aparecerá em negrito precedido por dois traços.          %
%   l(95): Use a função "\input{file}" (preferencialmente) ou escreva o texto dos Agradecimentos. %
%   l(96): Use a função "\input{file}" (preferencialmente) ou escreva o texto do Resumo.          %
%   l(97): Use a função "\input{file}" (preferencialmente) ou escreva o texto do Abstract.        %
%   l(98): Use a função "\input{file}" (preferencialmente) ou escreva o texto do Prefácio. Se vo- %
% cê optar por não ter um Prefácio, comente essa linha e também a l(109).                         %
%   l(102): Invocação da estrutura da capa (obrigatória).                                         %
%   l(103): Invocação da estrutura da folha de rosto (obrigatória).                               %
%   l(104): Invocação da estrutura da folha de aprovação (obrigatória apenas na versão final).    %
%   l(105): Invocação da estrutura da dedicatória (opcional, comente se preferir não usar).       %
%   l(106): Invocação da estrutura dos agradecimentos (opcional, comente se preferir não usar).   %
%   l(107): Invocação da estrutura da epígrafe (opcional, comente se preferir não usar).          %
%   l(108): Invocação da estrutura do resumos em português  e inglês (obrigatório). Usa espaça-   %
% mento simples como sugerem as normas da ABNT.                                                   %
%   l(109): Invocação da estrutura do prefácio (opcional, comente se preferir não usar).          %
%   l(110): Invocação da estrutura do sumário (obrigatório).                                      %
%   l(111): Inclua nesta linha outras listas (figuras, tabelas, abreviaturas, simbolos, etc) que  %
% estejam sendo usadas no seu trabalho (elementos opcionais).                                     %
%   l(113): Início da numeração arábica das páginas e dos Elementos Texuais. A partir daqui, es-  %
% colha entre escrever o conteúdo diretamente neste arquivo ou usar a função "\input{file}" para  %
% incluí-lo (preferencialmente).                                                                  %
%   l(135): Informe o nome do arquivo BibTeX (*.bib) de referências.                              %
%   l(136): Informe o estilo de apresentação das referências.                                     %
%   l(137): Se você optar por inserir as referências manualmente (ou copiar o arquivo *.bbl), co- %
% mente l(135) e l(136) e descomente o ambiente "thebibliography" l(137), l(138) e l(139).        %
%   l(140): Início dos Apêndices, identificados com letras. Escreva o conteúdo diretamente neste  %
% arquivo ou usar a função "\input{file}" para incluí-lo.                                         %
%                                                                                                 %
%                                       That's all, folks!                                        %
%                                   May the Force be with you.                                    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[twoside,openright,12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{times}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CARREGANDO PREÂMBULO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{preamble.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% INFORMAÇÕES GERAIS DA TESE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tipo
\tipo{Dissertation} \grau{Doctor of Philosophy}
%\tipo{Thesis} \grau{Master}


\titulo{~\\Search for NuMI $\mu$DAR Electron Neutrinos in MicroBooNE}
%\newtoks\subtitulo \subtitulo{Morte e Obra} 
\autor{Ohana Benevides Rodrigues}
\coorientador{}
\orientador{Professor Mitchell Soderberg}
\cidade{Syracuse - NY}
\ano{2022}
\data{September 02}

\dedicatoria{To my parents, Andrea de Fátima Benevides and Luis Claudio Rocha Rodrigues.}

\epigrafe{Knowledge emerges only through invention and reinvention, through the restless, impatient, continuing, hopeful inquiry human beings pursue in the world, with the world, and with each other.}
\autordaepigrafe{Paulo Freire}

\agradecimentoingles{For this work to be complete, it took a village. This acknowledgment section will not be short, but I see it as the most meaningful part of this work. The most valuable thing my Ph.D. brought were incredible mentors and friends, and being able to recognize the invisible cost my career took on my family. Let's get started.

When I first left home for college at 17 years old, I didn't know the costs of sustaining a career further and further away from my family. I didn't think it would cost me a complete lack of a local support system at times and not being home on happy days and sad ones. I didn't know I wouldn't be there when my parents were sick, to see my sisters go to college, or to see my baby brother grow up. But my parents knew exactly the cost. They knew that the cost for me to pursue my dream of becoming a scientist would be them not having the constant presence of their firstborn in their lives. So, first and foremost, I would like to thank my parents, Andrea and Luis Claudio, for loving and supporting me unconditionally. 

Next, I want to thank my siblings, Natasha, Duda, Sophia, and Heitor. I hope you know that I love you even if I am not there to guide you through the ups and downs of life. 

To my grandmother, Wallenir, who always loved me immensely. 

I would like to thank my life partner, Stefano Tognini, for being here for me every day. For choosing to navigate this life with me at its best and worst. You are the best partner I could ask for, and I love you. 

To Maria da Graça Tognini and Pier Angelo Tognini, who always treated me as their own daughter and provided all the support necessary for me to start this journey. 

To Mônica Nunes, the sister life brought me, who was always there for me for everything. 

I want to thank my advisor, Mitch Soderberg, for guiding and supporting me through my Ph.D. while respecting my individuality.

To Walter Freeman, whose mentorship and friendship helped me grow immensely. Walter met me as a scared, defensive, confused graduate student and helped me become a better instructor, researcher, and human. I am infinitely glad to be able to call him one of my dearest friends. 

To Andre Anselmo and Merrill Asp, the brothers Syracuse brought me. I wouldn't have survived those first years of graduate school without them. 

Many colleagues were responsible for making my days in Syracuse lighter, but I would like to explicitly mention thank Nicholas Didio, Varun Srivastava, Ellie Dawson, Chaitanya Afle, and Alex Pustelnyk.  

To Steven Gardiner, the person who imagined this project and contaminated me with his passion for it. He was fully hands-on on each step of this work, and it is just as his as mine. Beyond that, thank you for being such a kind and generous friend. 

This analysis was challenging to begin with, even more so during a pandemic. Many MicroBooNE collaborators helped me to get the resources and ideas I needed. I especially want to thank Ivan Lepetic, Elena Gramellini, David Caratelli, Krishan Mistry, William Foreman, and Kirsty Duffy. 

The SBND assembly and installation work was my Ph.D.'s most busy and fun work, and the long hours wouldn't be so light wasn't for the lightheartedness, generosity, and patience of Nicola McConkey, Anne Schukraft, Roberto Acciarri, Heriques Frandini, and John Najdzion.

To my best squad Afroditi Papadopoulou, Lauren Yates, and Erin Yandel, who provided all kinds of support, from technical to emotional. I am the luckiest person to have you. 

Lastly, to my beloved dogs, Rum and Quanta, that took me for walks, gave me love, and kept me going in my darkest moments.}

\agradecimento{

Os agradecimentos.

}

\abstract{Muon Decay-at-Rest ($\mu$DAR) produces electron-neutrinos ($\nu_e$) in the $0$ to $53$ MeV energy range. The given range is especially interesting for its similarity to Supernovae-produced $\nu_e$. The Deep Underground Neutrino Experiment (DUNE) has as one of its main goals to measure Supernovae neutrinos on the occasion of a Galactic Supernova burst. To optimize the chances of detection, a low-energy neutrino-LAr cross-section (XS) measurement is a piece of important information to have at hand. MicroBooNE presents a good opportunity to explore the low-energy $\nu$-LAr detection and XS using the $\mu$DAR neutrinos and therefore develop the tools necessary for DUNE to interpret the results of a supernova neutrino detection.
MicroBooNE is a LArTPC that has been collecting neutrino data since October 2015 from the Booster Neutrino Beam (BNB) and off-axis to the Neutrinos at the Main Injector (NuMI) beam, both copious sources of $\mu$DAR neutrinos. 
In this thesis, we present a first attempt to measure MeV-scale neutrinos in a LArTPC. To do that, we use especific MeV-scale reconstruction tools combined with other traditional reconstruction tools used in MicroBooNE. We discuss the tool's performance, limitations, and provide suggestions on how to improve them.
This analyzes looks for $\mu$DAR neutrino- argon charged current interactions in the NuMI Run1 data, that contains $2\times 10^{20}$ POT. We observed $9,176$ signal candidates. The number of expected background events is $8,776$, the majority from cosmic rays. We establish a XS upper limit of $<\sigma> = 1.99\times10^{-37} \textrm{cm}^2 / \textrm{Ar}$, which corresponds to $551.9$ times the nominal prediction from MARLEY, the neutrino generator used in this work. Despite the lack of sensitivity, this work is the first of its kind and sets the foundation for future similar analysis in the future. In the conclusions, we discuss how this results can be further improved in MicroBooNE.}

%\prefacio{\lipsum[1-3]}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PRÓLOGO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\capa
%\paginaTECA
%\folhaderosto
%\paginaFichaCatalografica
%\folhadeaprovacao
\adedicatoria
\notaagradecimentoingles
%\notaagradecimento
\acitacao
\resumos
%\apresentacao
\tableofcontents
\listoffigures 
\listoftables
\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CORPO DA TESE/DISSERTAÇÃO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\inicio

\chapter{Introduction}
\input{Chapters/1.tex}

\chapter{Liquid Argon Time Projection Chambers in Neutrino Physics}
\input{Chapters/2.tex}

\chapter{The MicroBooNE Experiment}
\input{Chapters/3.tex}

\chapter{$\mu$ Decay At Rest $\nu_{e}$ Search in MicroBooNE}
\input{Chapters/4.tex}

\chapter{Conclusion}
\input{Chapters/5.tex}

\chapter{Short Baseline Neutrino Detector's Anode Plane Assemblies Assembly and Installation}
\input{Chapters/6.tex}

% Apêndices
\appendix % Não deletar
\isappendixtrue % Não deletar
%\renewcommand\chaptername{Appendix}

%\chapter{An appendix title}
%\input{Appendices/A.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EPÍLOGO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{References}

\bibliographystyle{unsrt}

\begin{thebibliography}{10}

% Escreva um simples arquivo com referências ou insira  o .bbl
\input{References/R1.tex}
\input{References/R2.tex}
\input{References/R3.tex}
\input{References/R4.tex}
\input{References/R5.tex}

\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FIM DO DOCUMENTO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}