%[1]
\bibitem{microboone_electronics} R. Acciarri, \textit{et al.} \textbf{Noise Characterization and Filtering in the MicroBooNE Liquid Argon TPC}. JINST 12 P08003. 2017.

%[2]
\bibitem{microboone_design} R. Acciarri, \textit{et al.} \textbf{Design and construction of the MicroBooNE detector}. JINST 12 P02017. 2017. 

%[3]
\bibitem{lar_excimers} W. Pontseele. \textbf{Search for Electron Neutrino Anomalies with the MicroBooNE Detector}. PhD thesis, Oxford U., 2020.

%[4]
\bibitem{uboone_pmt} Microboone photomultiplier. \href{https://news.fnal.gov/2015/07/microboone- photomultiplier/}{https://news.fnal.gov/2015/07/microboone- photomultiplier/}.

%[5]
\bibitem{RFQ_website} J. Orwig, \textbf{Cockcroft-Walton's successor: a peep inside the new RFQ and how it works}. 2012. Retrieved from http://www.fnal.gov/pub/today/archive/archive\_2012/today12-11-02\_RFQReadmore.html

%[6]
\bibitem{LINAC_website} \textbf{Fermilab Linac}. Retrieved from \url{http://www-bd.fnal.gov/proton/linac.html/}

\bibitem{booster_website} \textbf{Booster Department}. Retrieved from http://www-ad.fnal.gov/proton/booster.html

\bibitem{paper_numibeamline} P. Adamson, \textit{et al.} (MINOS Collaboration) \textbf{The NuMI neutrino beam}. Nucl. Instr. Meth. A \textbf{806}, 279-306. 2016.

%[7]
\bibitem{numi} \textbf(Target Systems). Retrieved from \url{https://targets.fnal.gov/NuMI_neutrino_beam.html}

%[8]
\bibitem{krish_phd} K. Mistry, \textbf{First Measurement of the Flux-Averaged Differential Charged-Current Electron-Neutrino and Antineutrino Cross Section on Argon with the MicroBooNE Detector}. PhD thesis, U. of Manchester, 2021. 

%[10]
\bibitem{numi_redmine} MicroBooNE Collaboration, \textbf{NuMI Documentation}. Internal Documentation. Retrieved from \url{https://cdcvs.fnal.gov/redmine/projects/uboone- physics-analysis/wiki/NuMI_Documentation#Using- NuMI-samples-for-an-analyser}. 